Agile Methods and Model Driven Engineering: a survey

### 2017-12-07 article.tex
Unescaped % sign...

The combination of agile methods with MDD approaches in this case study had positive outcomes as follows. First, due to the code generation capacity of MDD, 93% of the entire component code was automatically generated leading to an increase in productivity of the workers as they realised a three-fold increase in source code lines per staff month as compared with hand coding. Secondly, the quality of the automatically generated code in terms of defects density was significantly higher than manual code.

>>>>

The combination of agile methods with MDD approaches in this case study had positive outcomes as follows. First, due to the code generation capacity of MDD, 93\% of the entire component code was automatically generated leading to an increase in productivity of the workers as they realised a three-fold increase in source code lines per staff month as compared with hand coding. Secondly, the quality of the automatically generated code in terms of defects density was significantly higher than manual code.
